Introduction

### 2016-04-29 dissertation/papersincontext.tex
contributions of two first papers

@@

>>>>

Main contributions:
\begin{enumerate}
\item A thorough discussion of the implications of Hypermedia
  Types\cite{hypermediatypes} for RDF.
\item A sketch of a vocabulary for read-write RDF hypermedia.
\end{enumerate}

@@

Main contributions:
\begin{enumerate}
\item Introduction of a path to critical practice of evaluations, that makes
  use of contemporary statistical techniques, to establish a practice
  that can be used to refute assertions on performance.
\item A didactical experiment to help researchers understand the statistics.
\item The novel application of a well established method in
  statistics, rarely used in Computer Science, to SPARQL endpoint
  evaluation.

\end{enumerate}
